\LARGE \bf Multi-Armed Bandit Models for Sample-Based Grasp Planning in the Presence of Uncertainty [v-14 09-30-2014]

### 2014-10-02 paper.tex
changed n to l for GP

\subsection{Gaussian Process (GP) Background}
Given the training data $\mD = \{\mX, \by\}$ and covariance function $k(\cdot,\cdot)$, the posterior density $p(sd_*|\bx_*,\mD)$ at a test point $\bx_{*}$ is shown to be \cite{rasmussen2010gaussian}:
\begin{align*}
	p(sd_*|\bx_*,\mD) &\sim \mN\big(\mu(\bx_*), \Sigma(\bx_*)\big) \\
	\mu(\bx_*) &= k(\mX,\bx_*)^{\intercal}(K + \sigma^2I)^{-1}\by \\
	\Sigma(\bx_*) &= k(\bx_*,\bx_*)-k(\mX,\bx_*)^{\intercal}(K+\sigma^2I)^{-1}k(\mX,\bx_*)\big) 
\end{align*}
where $K \in \mathbb{R}^{n \times n}$ is a matrix with entries $K_{ij} = k(\bx_i,\bx_j)$ and $k(\mX,\bx_*) = [k(\bx_1,\bx_*),\ldots,k(\bx_n,\bx_*)]^{\intercal}$. 
This derivation can also be used to predict the mean and variance of the function gradient by extending the kernel matrices using the identities \cite{solak2003derivative}:

>>>>

\subsection{Gaussian Process (GP) Background}
Given the training data $\mD = \{\mX, \by\}$ and covariance function $k(\cdot,\cdot)$, the posterior density $p(sd_*|\bx_*,\mD)$ at a test point $\bx_{*}$ is shown to be \cite{rasmussen2010gaussian}:
\begin{align*}
	p(sd_*|\bx_*,\mD) &\sim \mN\big(\mu(\bx_*), \Sigma(\bx_*)\big) \\
	\mu(\bx_*) &= k(\mX,\bx_*)^{\intercal}(K + \sigma^2I)^{-1}\by \\
	\Sigma(\bx_*) &= k(\bx_*,\bx_*)-k(\mX,\bx_*)^{\intercal}(K+\sigma^2I)^{-1}k(\mX,\bx_*)\big) 
\end{align*}
where $K \in \mathbb{R}^{l \times l}$ is a matrix with entries $K_{ij} = k(\bx_i,\bx_j)$ and $k(\mX,\bx_*) = [k(\bx_1,\bx_*),\ldots,k(\bx_l,\bx_*)]^{\intercal}$. 
This derivation can also be used to predict the mean and variance of the function gradient by extending the kernel matrices using the identities \cite{solak2003derivative}:
